Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-13 paper/paper.tex
misc
update code code; minor revision

The function @choices@ takes two arguments: a set of elements with type @T@, 
and an initial accumulated value of type @Ans@.
The @choices@ iteratively returns an element from the collection along with the 
latest cache, and the return type is also annotated by \verb|@cps[Ans]|. 
This annotation denotes the final returned value of @choices@ is type @Ans@.
The @f@ is the delimited continuation captured by the @shift@ operator, which
is form by the statements after @choices@'s call-site.

@@

\textit{Abstract Interpretation and Control-Flow Analysis.}
\citeauthor{cousot1977abstract} invented abstract interpretation as a sound approach
to approximate a program's runtime behavior\cite{cousot1977abstract}.
Control-flow analysis is one instance of abstract interpretation on functional programs
that can be traced to Jones \cite{jones1981flow}.
\citeauthor{Shivers:1988:CFA:53990.54007} introduces $k$-CFA which uses $k$ recent calling
contexts as program contour that differentiates values from different contexts 
\cite{Shivers:1988:CFA:53990.54007, Shivers:1991:SSC:115865.115884}.
The modern formulation of control-flow analysis is the abstracting abstract machines
methodology \cite{van2012systematic, van2010abstracting} which forms the starting point
of this paper.
Modern programming languages such as Java\cite{might2010resolving} and Racket 
\cite{Tobin-Hochstadt:2012:HSE:2384616.2384655}
can also be modeled by the abstracting abstract machine approach. \\

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}

>>>>

The function @choices@ takes two arguments: a set of elements with type @T@, 
and an initial accumulated value of type @Ans@.
The @choices@ iteratively returns an element from the collection along with the 
latest cache, and the return type is also annotated by \verb|@cps[Ans]|. 
This annotation denotes the final returned value of @choices@ is type @Ans@.
The @f@ is the delimited continuation captured by the @shift@ operator, which
is formed by the statements after @choices@'s call-site.

@@

\textit{Abstract Interpretation and Control-Flow Analysis.}
\citeauthor{cousot1977abstract} invented abstract interpretation as a sound approach
to approximate a program's runtime behavior\cite{cousot1977abstract}.
Control-flow analysis is one instance of abstract interpretation on functional programs
that can be traced to Jones \cite{jones1981flow}. \citeauthor{Shivers:1988:CFA:53990.54007} 
introduces $k$-CFA which uses $k$ recent calling contexts as program contour that 
differentiates values from different contexts \cite{Shivers:1988:CFA:53990.54007, 
Shivers:1991:SSC:115865.115884}.
The recent formulation of control-flow analysis is the abstracting abstract machines
methodology \cite{van2012systematic, van2010abstracting} which forms the starting point
of this paper.
Modern programming languages such as Java\cite{might2010resolving} and Racket 
\cite{Tobin-Hochstadt:2012:HSE:2384616.2384655}
can also be modeled by the abstracting abstract machine approach. \\

@@

%% TODO: Acknowledgments
\begin{acks}                            %% acks environment is optional
                                        %% contents suppressed with 'anonymous'
  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
  %% acknowledge financial support and will be used by metadata
  %% extraction tools.
  This material is based upon work supported by the
  \grantsponsor{GS100000001}{National Science
    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
  conclusions or recommendations expressed in this material are those
  of the author and do not necessarily reflect the views of the
  National Science Foundation.
\end{acks}
